Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 result_discussion.tex
fix typos

Our algorithm's payment is constant in $T$,
while its regret is $O(\log^3(T))$ in general with a lower bound of
$\Omega(\log(T))$;
when preferences are discrete, our algorithm's regret is
constant in $T$.
Thus, viewed solely in terms of the dependence on $T$,
the best performance achievable seems comparable to that in a standard
multi-armed bandit problem;
but when preferences our discrete, the constant regret (rather than
$\Theta(\log T)$ surpasses a standard multi-armed bandit.
This may seem surprising, because our setting is one in which the
principal has both less control and less information than in the
standard bandit setting.
The result arises because heterogeneity in preferences indeed provides
free exploration, in which all of the arms can be pulled infinitely
often without incurring regret.

While heterogeneity in preferences enables this free exploration,
heterogeneity alone is not always sufficient for enabling performance
improvements compare to the standard bandit setting.
Indeed, consider a version in which agents are still heterogeneous,
but the principal has the power to pull arms directly.
Unless the heterogeneity can be observed (i.e., the principal knows
the agents' types), the principal will be unable to correctly choose
each agent's preferred arm,
even with infinite exploration of arm attributes.
Hence, in this setting, the regret will grow as $\Omega(T)$.

>>>>

Our algorithm's payment is constant in $T$,
while its regret is $O(\log^3(T))$ in general with a lower bound of
$\Omega(\log(T))$;
when preferences are discrete, our algorithm's regret is
constant in $T$.
Thus, viewed solely in terms of the dependence on $T$,
the best performance achievable seems comparable to that in a standard
multi-armed bandit problem;
but when preferences our discrete, the constant regret (rather than
$\Theta(\log T)$) surpasses a standard multi-armed bandit.
This may seem surprising, because our setting is one in which the
principal has both less control and less information than in the
standard bandit setting.
The result arises because heterogeneity in preferences indeed provides
free exploration, in which all of the arms can be pulled infinitely
often without incurring regret.

While heterogeneity in preferences enables this free exploration,
heterogeneity alone is not always sufficient for enabling performance
improvements compared to the standard bandit setting.
Indeed, consider a version in which agents are still heterogeneous,
but the principal has the power to pull arms directly.
Unless the heterogeneity can be observed (i.e., the principal knows
the agents' types), the principal will be unable to correctly choose
each agent's preferred arm,
even with infinite exploration of arm attributes.
Hence, in this setting, the regret will grow as $\Omega(T)$.
